Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-12-15 Paper/ms.tex
New figures, fake data results
Fake data truth

\section{Demonstration on Simulated Data}
To test our proposed methodology, we generated a simulated dataset for a
system with $N=5$ planets. The dataset was ``inspired by'' the $\nu$ Oph
dataset (Section~\ref{sec:nu_oph}), and contains two large signals with
periods of 531 and 3180 days, whose semi-amplitudes are
322 ms$^{-1}$ and 214 ms$^{-1}$ respectively. The other three planets have
much lower semi-amplitudes, ranging from 1-9 ms$^{-1}$. The standard deviation
for the noise in the data was 5 ms$^{-1}$, so some of these low-amplitude
signals should be detectable. The simulated data is shown in
Figure~\ref{fig:fake_data}, along with a model fit.

@@

>>>>

\section{Demonstration on Simulated Data}
To test our proposed methodology, we generated a simulated dataset for a
system with $N=5$ planets. The dataset was ``inspired by'' the $\nu$ Oph
dataset (Section~\ref{sec:nu_oph}), and contains two large signals with
periods of 531 and 3180 days, whose semi-amplitudes are
322 ms$^{-1}$ and 214 ms$^{-1}$ respectively. The other three planets have
much lower semi-amplitudes, ranging from 1-9 ms$^{-1}$. The standard deviation
for the noise in the data was 5 ms$^{-1}$, so some of these low-amplitude
signals should be detectable. The simulated data is shown in
Figure~\ref{fig:fake_data}, along with the true radial velocity curve $m(t)$
that was used to generate the data.

@@

\begin{figure}
\includegraphics[scale=0.4]{Figures/fake_data_N.eps}
\caption{\label{fig:fake_data_N}}
\end{figure}

\begin{figure}
\includegraphics[scale=0.4]{Figures/fake_data_periods.eps}
\caption{\label{fig:fake_data_periods}}
\end{figure}

\begin{figure}
\includegraphics[scale=0.4]{Figures/fake_data_posterior.eps}
\caption{\label{fig:fake_data_posterior}}
\end{figure}
